Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-09 src/tex/ms.tex
Complete flowMC part

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{color}

@@

\subsection{Normalizing Flow}
\label{sec:flow}

@@

% How does it help our sampling
As mentioned in the previous subsection, one of the main issue gradient-based
sampler is it does not explore local correlation and multi-modality well. This
is exactly where the normalizing flow model can help. While the method would
still work when there is only one independent local sampler chain, this method
works much better when we employ a lot of independent chains. By looking across
multiple chains, the normalizing flow learns the global landscape of the target
distribution, hence we can use it as a \textit{proposal} distribution. This
means independent chains can now jump between modes, or within a single mode
that exhibits complex geometry that cannot be handled easily only through the
local sampler, which greatly reduce both the burn-in time and sampling time.

% Write down how you use it as proposal

\begin{align}
    acc(x,x_0) = \rm{min} \left[ 1, \frac{\hat{\rho}(x_0)\rho_*(x)}{\hat{\rho}(x)\rho_*(x_0)}\right],
\end{align}
where $x = f(z), z \sim p_z(Z)$ is the proposed jump location and $x_0$ is the current position.
We can see the flow distribution is the target distribution when the accepting probability is 1.

\kw{Mention how this helps gravitational wave, gives examples.}

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color}

@@

\subsection{Normalizing Flow enhanced sampling}
\label{sec:flow}

@@

% The flowMC algorithm
As mentioned in the previous subsection, one of the main issue gradient-based
sampler is it does not explore local correlated features and multi-modality well. This
is exactly where the normalizing flow model can help. Once multiple independent
chains have generated samples, we can combine the samples and feed it to the
normalizing flow, which it learns the global landscape of the target
distribution. Note that since the independent chains are generated with the same
number of samples, the normalization between posterior density represented by
different chains are in general different from the true target distribution. To
adjust for this inaccuracy, we use the normalizing flow model as a
\textit{proposal} distribution. Given a trained normalizing flow model, we can
generate proposed jump in the target space by sampling from the latent
distribution $z \sim p_z(Z)$, then push it through the learned map given by the
normalizing flow model $x=f(z)$. the acceptance criteria is given by
\begin{align}
    \alpha(\mathbf{x},\mathbf{x_0}) = \min \left[ 1, \frac{\hat{\rho}(\mathbf{x_0})\rho_*(\mathbf{x})}{\hat{\rho}(\mathbf{x})\rho_*(\mathbf{x_0})}\right],
\end{align}
where $\hat{\rho}$ is probability density estimated by the normalizing flow
model, $\rho_*$ is the probability density evaluated using the target function,
and $x_0$ is the current position. We can see the flow distribution is the
target distribution when the accepting probability is 1. When the normalizing
flow model has not converged to the target distribution, only a portion of the
proposed jumps will be accepted. This means MCMC process using the normalizing
flow model as the proposal distribution can adjust the normalization across
different regions of the target parameter space by rejecting jumps into less
likely regions. The training and sampling is then repeated until a certain
criteria is met. Note that everytime we retrain the network, we are breaking the
Markov properties since we are changing the proposal distribution. To produce
final samples that can be used to estimate target quantities, one has to freeze
the normalizing flow model and does not retrain during the final sampling phase.
To summarize the sampling process, the pseudocode is given by

\begin{algorithm}
\caption{An algorithm with caption}\label{alg:cap}
\KwData{Initial position}
\KwResult{Chains, $\log{\mathcal{L}}$}
\emph{Training}\;
% \While{not converged}{
%     \For{n_loc}{

%     }
%     Local Sampling
% }
\emph{Production}\;
\end{algorithm}

% Move these to discussion

This means independent chains can now jump between modes, or within a single
mode that exhibits complex geometry that cannot be handled only through the
local sampler, which greatly reduce both the burn-in time and sampling time.

While the method would still work when there is only one independent local
sampler chain, this method works much better when we employ a lot of independent
chains because of the increased number of samples available for training. 
\kw{Mention how this helps gravitational wave, gives examples.}

In practice, we find the normalizing flow not only helps jumping betw
